### 2024-05-29 getting-started.qmd
20240528 - edit for consistency

players[,c(2,3)]
players[,c("name","age")]
players[,subsetVars]
```

@@

players[,-c(2,3)]
players[,!(names(players) %in% c("name","age"))]
players[,!(names(players) %in% dropVars)]
```

>>>>

players[,c(2,4)]
players[,c("name","age")]
players[,subsetVars]
```

@@

players[,-c(2,4)]
players[,!(names(players) %in% c("name","age"))]
players[,!(names(players) %in% dropVars)]
```
